\subsection{Contributions}
We bridge the gap \stefan{you have not really established this gap yet: is there not quite a bit of theory on random beacons already? can you quickly review it and then say why it is "too theoretical"?} between theoretical solutions and the real world by designing and implementing a secure, trust-minimizing randomness beacon based on the transparent authority model with user input.
The design is based on a structured analysis of threats to a randomness beacon.
We design the beacon from the ground up based on tried and tested methods as well as novel ideas.
Specifically, we differ from previous transparent authority approaches by the following:
\begin{itemize}
    \item We describe a novel way of parallelizing the beacon pipeline to provide a higher trust probability.
    \item Unlike all other approaches we have seen, the beacon operator in our beacon design has no private information --- all inputs are hashed and are released to the public in batches.
    \item We choose to use Merkle trees as the data structure for inputs.
    \item We allow multiple input channels and output channels to be instantiated for reliability, distribution of workload, easy scaling, and convenience for the users.
\end{itemize}
Combined, our novel ideas significantly decreases the need for blind trust and limits the severity of a myriad of attacks.
Lastly, we explore usage of our beacon in context. As such, we describe several use cases and how the beacon output is used as a cryptographic primitive in a way that aligns with and extends our security goals.
\stefan{What about performance analysis?}
