\section{Conclusion}%
\label{sec:conclusion}

% Rehash the problem
% But under no circumstance just copy something from the introduction or abstract.
% Now it is usually possible to use concrete numbers and terminology.
This work was based partly on interest in randomness beacons, and partly on wondering why these services are not implemented for real world usage.

While we took inspiration from previous work and literature, designing a randomness beacon from scratch was no simple feat.
We designed a system which is based on simple and succinct principles.
However, simple systems still have many details in their implementation.
We made conscious choices regarding communication framework, communication patterns, compromises between verbosity and bare essentials in communication, and put a lot of thought into the practicalities of deploying and operating our beacon.
In particular, we parallelized the beacon operation to have a continuous input stream and regular output, and outlined a formula for finding the number of computation nodes.
We also scaled input collection by enabling horizontal scaling, and improved usability of the system by allowing these input collectors to collect from a variety of sources with easy access for users.

We showed the possibility of instantiating a randomness beacon with sensible guarantees for any single user; i.e.\ given their random input to the beacon, they can easily and rapidly verify the computation, and decide if they deem it trustworthy.

% Rehash our contributions --- what is significant?
We performed a security analysis of randomness beacons to identify threats towards them, and incorporated counter measures for them in the design of our own beacon.
Some threats were impossible to counter, and these were discussed.

We refined and extended the work of \citet{randomzoo}, who propose a delay function and provide a short discussion on the repercussions of the users' trust assumptions by using a delay function.
Our refinement allows all users to run the delay function in parallel with the beacon operator, or to run it if the beacon operator (maliciously or not) performs an output withholding attack.
We extended the discussion of users' trust assumptions by providing a succinct formula, which only depends on two timestamps and what the user believes is the fastest possible computation of a given delay function.

Further, we have proposed a parallelization technique for the beacon pipeline, such that input collection is a continuous stream.
This allows the output frequency to be considerably increased, and enables adjustments to the ratio between input collection time and computation time.
Simultaneously, we noted that computation components can be reused for subsequent computations instead of instantiating new services, thereby removing startup time.
For redundancy, reducing bottlenecks, and usability we allow multiple input and output channels.

We also explored the applications of our randomness beacon as a cryptographic primitive in a variety of use cases.
We presented ceremonies for using our beacon to securely obtain public randomness.
The use cases range from lotteries to crypto system bootstrapping, and each has a ceremony associated with it.
As such, we not only investigated the gap in literature of a practical beacon implementation, but also discussed the practicality of the beacon in context.

% Assess the significance of contribution
We believe our contributions fills a hole in current literature, and as such can be seen as a step forward.
It is, however, clear that there is need for more work that is not necessarily technical in nature.
No matter how much we believe in randomness beacons as a concept, it might prove hard to convince users to use a beacon.
While we argued that the beacon is not necessarily expensive to run for the beacon operator, incentives to run a beacon still needs further thought.
Finally, usability of the beacon needs to be improved if we expect normal users to use it.

% Societal perspective! Trust in the future is increasingly important
In the future, trusting any entity with decisions will, in our opinion, be more far-reaching than it is today.
We see more and more corporate giants virtually controlling whole industries.
Before empowering a few world-wide corporations to make decisions that affect us, we, as normal users in society, need ways to ensure fairness.
Randomness beacons might be one such way.
